Simulation Study: Informative Covariate (step)

### 2018-04-01 datasets/simulations/simulations-informative-cubic.Rmd
Add step-func cov sim; increase singal size

```{r gauss-parameters}
tstat <- rnorm_generator(2)       # functional: dist of alternative test stats
tstat_dist <- rnorm_perturber(1)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)    # functional: dist to calc p-values
seed <- 608
```

@@

We plot the averaged results across `r B` simulations.

@@

```{r t5-parameters}
tstat <- rnorm_generator(5)    # functional: dist of alternative test stats
tstat_dist <- rt_perturber(5)  # functional: sampling dist/noise for test stats
null_dist <- rt_2pvaluer(5)    # functional: dist to calc p-values
seed <- 815
```

@@

>>>>

```{r gauss-parameters}
tstat <- rnorm_generator(3)       # functional: dist of alternative test stats
tstat_dist <- rnorm_perturber(1)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)    # functional: dist to calc p-values
seed <- 608
```

@@

We plot the averaged results across `r B` replications.

@@

```{r t5-parameters}
tstat <- rnorm_generator(6)    # functional: dist of alternative test stats
tstat_dist <- rt_perturber(5)  # functional: sampling dist/noise for test stats
null_dist <- rt_2pvaluer(5)    # functional: dist to calc p-values
seed <- 815
```

@@

plotsim_average(resdf, met = "rejections", filter_set = excludeSet,
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "FDR", filter_set = excludeSet,
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "TPR", filter_set = excludeSet,
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "TNR", filter_set = excludeSet,
                merge_ihw = TRUE, errorBars = TRUE) 
```

Since both `scott-empirical` and `scott-theoretical` are not appropriate when
the test statistics are not approximately normal, we also plot the results without
these methods.

```{r chisq4-metrics-averages-nofdrreg, results = "hide"}
plotsim_average(resdf, met = "rejections",
                filter_set = c(excludeSet, "scott-empirical", "scott-theoretical"),
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "FDR",
                filter_set = c(excludeSet, "scott-empirical", "scott-theoretical"),
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "TPR",
                filter_set = c(excludeSet, "scott-empirical", "scott-theoretical"),
                merge_ihw = TRUE, errorBars = TRUE)

plotsim_average(resdf, met = "TNR",
                filter_set = c(excludeSet, "scott-empirical", "scott-theoretical"),
                merge_ihw = TRUE, errorBars = TRUE) 
```

### 2018-04-01 datasets/simulations/simulations-informative-step.Rmd
Add step-func cov sim; increase singal size

---
title: "Simulation Study: Informative Covariate (sine)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with an informative covariate. The covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a smooth (sine) function of the covariate. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed noise.

@@

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-sine-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-sine-benchmark-t5.rds")
chisq_file <- file.path(resdir, "informative-sine-benchmark-chisq4.rds")

@@

```{r parameters-shared}
m <- 20000                        # integer: number of hypothesis tests
pi0 <- pi0_sine(0.90)             # numeric: proportion of null hypotheses
icovariate <- runif               # functional: independent covariate
```

>>>>

---
title: "Simulation Study: Informative Covariate (step)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with an informative covariate. The covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a non-smooth (monotone) step function of the covariate. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed noise.

@@

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-step-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-step-benchmark-t5.rds")
chisq_file <- file.path(resdir, "informative-step-benchmark-chisq4.rds")

@@

```{r parameters-shared}
m <- 20000                        # integer: number of hypothesis tests
pi0 <- pi0_step(0.90)             # numeric: proportion of null hypotheses
icovariate <- runif               # functional: independent covariate
```
